Experience Report: Haskell in Computational Biology

### 2012-03-12 mrfy_experience_report.tex
turned doco paragraph into one sentence about examples

You~also need to know that while the Haskell community offers many
enticing tools, libraries, and packages,
not all of them are worth using.
Some are not ready for prime time, and some were once great but are
no~longer maintained.
The great packages, like \texttt{Data.Memocombinators} and Parallel
Strategies, are truly great.
But~for amateurs, it's not always easy to tell them from the wannabes
and the has-beens.

Most of the software we used came from Hackage, which is the Haskell
community's software repository.
We~sometimes found it hard to tell
if a particular Hackage package was right for us.
In particular, as beginning 
functional programmers, we~found some documentation inaccessible.
The documentation that we found most accessible typically contained
examples showing how to use a particular tool or library.
\remark{So what's our message here? What are we telling people to
think or do differently? ---NR}

>>>>

You~also need to know that while the Haskell community offers many
enticing tools, libraries, and packages,
not all of them are worth using.
Some are not ready for prime time, and some were once great but are
no~longer maintained.
The great packages, like \texttt{Data.Memocombinators} and Parallel
Strategies, are truly great.
But~for amateurs, it's not always easy to tell the great packages from the wannabes
and the has-beens.
And even some of the great packages could be better documented, with
more examples.

%%  Most of the software we used came from Hackage, which is the Haskell
%%  community's software repository.
%%  We~sometimes found it hard to tell
%%  if a particular Hackage package was right for us.
%%  In particular, as beginning 
%%  functional programmers, we~found some documentation inaccessible.
%%  The documentation that we found most accessible typically contained
%%  examples showing how to use a particular tool or library.
%%  \remark{So what's our message here? What are we telling people to
%%  think or do differently? ---NR}
